Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-08 ms/manuscript.Rmd
Add data availability statement
Change figure output to tiff
- as per New Phyt requirements

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/canopylife. Data have been deposited in Dryad (\*\*\* ADD DOI \*\*\*).

@@

```{r climate, fig.height = 4, fig.width = 6, fig.cap = "Microclimatic variables."}
climate_plot
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
```

@@

```{r cwm-div, fig.height = 4, fig.width = 8, fig.cap = "Community-weighted means."}
combined_cwm_plots
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
```

>>>>

### Data accessibility

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/canopylife. Raw and processed data are openly available from the Dryad repository at (http://doi.org/[\*\*\* ADD DOI \*\*\*]) [@Nitta2019].

@@

```{r climate, fig.height = 4, fig.width = 6, fig.cap = "Microclimatic variables."}
climate_plot
ggsave(plot = climate_plot, filename = here("ms/fig1.tiff"), height = 4, width = 6, units = "in", dpi = "retina")
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
ggsave(plot = pca_plot, filename = here("ms/fig2.tiff"), height = 6, width = 6, units = "in", dpi = "retina")
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
ggsave(plot = traits_with_tree, filename = here("ms/fig3.tiff"), height = 8, width = 6, units = "in", dpi = "retina")
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
ggsave(plot = importance_heatmap, filename = here("ms/fig4.tiff"), height = 4, width = 6, units = "in", dpi = "retina")
```

@@

```{r cwm-div, fig.height = 4, fig.width = 8, fig.cap = "Community-weighted means."}
combined_cwm_plots
ggsave(plot = combined_cwm_plots, filename = here("ms/fig5.tiff"), height = 4, width = 8, units = "in", dpi = "retina")
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
ggsave(plot = combined_comm_div_plots, filename = here("ms/fig6.tiff"), height = 8, width = 4, units = "in", dpi = "retina")
```
